A Comparison of Graph Processing Systems

### 2020-09-26 documentation/paper/sections/overview/gemini.tex
gemini writeup improvements

The real bottleneck of distributed systems is not the communication itself, but the extra instructions, as well as memory references and a lower usage of multiple cores compared to the shared memory counterparts.
There are four main reasons for this.
The first reason is the use of hash maps to convert the vertex IDs between the global and the local state.
The second reason is the maintenance of vertex replicas on the different systems.
Another reason is the communication-bound apply phase in GAS abstraction.
And the last reason is the lack of dynamic scheduling.

@@

Gemini is fairly lightweight and has a clearly defined API between the core framework and the implementations of the individual algorithms. The five already implemented algorithms are Single-Source SSSP, BFS, PR, Connected-Components (CC) and Betweenness-Centrality (BC).

>>>>

The real bottleneck of distributed systems is not the communication itself, but the extra instructions, as well as memory references and a lower usage of multiple cores compared to the shared memory counterparts.
There are three main reasons for this.
The first reason is the use of hash maps to convert the vertex IDs between the global and the local state.
Another reason is the maintenance of vertex replicas on the different systems.
And the last reason is the lack of dynamic scheduling.

@@

Gemini is fairly lightweight and has a clearly defined API between the core framework and the implementations of the individual algorithms.
It also provides standard implementations for the following algorithms Single-Source SSSP, Breadth-First Search (BFS), PageRank (PR), Connected-Components (CC) and Betweenness-Centrality (BC).
